I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-04-29 lipics-master/proofs.tex
update

We fix a target node $z$.
We now define the partial sign function $S^z$, denoted $S$ when $z$ is clear from the context:

\begin{definition}
	\label{sign_of_nodes}
	We define the partial sign function $S$ on node $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have weight $0$; 
		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

@@

\begin{proof}
	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same sign as $S(n)$. 
	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose sign is 
	$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
	\hfill $\square$
\end{proof}

@@

Using the concept of sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:

@@

	Let $n$ be node of the DNN. We set the target $z=n$ and consider the sign function $S^z=S^n=S$ corresponding to that node. By definition, $S(n)=1$.

@@

	\begin{proof}
		By contradiction, if there is a weak compensating pair of two paths, $\rho_1,\rho_2$, 
		then consider the common nodes by increasing layer $n_1 \cdots n_k$ in $\rho_1,\rho_2$ (including the initial and final nodes).
		Assume that there is no compensating pair.
		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same sign (they have no nodes in common but the initial and final nodes).
		Hence $\rho_1$ and $\rho_2$ have the same sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair. 
	\end{proof}

@@

			Recall the sign function of nodes from Definition \ref{sign_of_nodes}. 
			Because weakly compensating paths are allowed, the sign function is no longer defined on all nodes. $S$ is defined for all nodes from which there is no weakly compensating pairs of paths to $z$. In particular, $S$ is defined on all nodes of $I$.

@@

			\begin{proof}
				By contradiction, assume that there exists two paths $\rho_1,\rho_2$ from 
				$n$ to $z$ with (strictly) different signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. 
			\end{proof}

@@

				(2) If $S(c)=1$, then we have the following:	\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$. Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.

				Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$. Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same sign. And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions. Combining all these facts, we have:\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
					&constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
					= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
				\end{align*}  This is the first equal.

@@

\begin{proof}
Let $(s,t)$ be the source and the target of $(\rho_1,\rho_2)$.
Let an input $a$ such that $a<s$ with path $\rho_0$ between $a$ and $s$,
and $\rho_3$  from $t$ to $z$.
Applying (H1) to the pair 
$(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$, 
we have another (non zero weight) path $\rho'$ from $a$ to $z$ totally disjoint with these two path.
The weights of $(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$
are of opposite sign because $(\rho_1,\rho_2)$ is weakly compensating, so one of them must be of opposite sign than the weight of $\rho'$. Say its $\rho = \rho_0 \cdot \rho_1 \cdot \rho_3$
else we pick $\rho=\rho_0\cdot \rho_2 \cdot \rho_3$.
Then $(\rho,\rho')$ is a pair of compensating path from $a$ to $z$, and as $n$ is neither an input nor $z$, it is strictly on $\rho$.
\end{proof}

@@

			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
			wrt node $z$. As proved earlier, $Z$ is suffix closed, i.e. if $m<n<z$ with $m \in Z$, then $n \in Z$. We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign. They form 2 independent subnetworks of the DNN.
			$X$ can intersect both $Z_+$ and $Z_-$.
			For nodes not in $Z$: some may be in $X$, and some may be out of $X$.
			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.

			Because of (H1), nodes not in $Z$ (and not in the inputs) are in $X$:
			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight. Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$. We call $X_*$ this subset $X$.

\begin{lemma}
	\label{lemma10}
		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
		of paths  with weights of opposite sign with $\rho_1$ from $m$ to $y$ and 
		with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

\begin{proof}
  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
  Hence $\rho_1 \rho, \rho_2$ have opposite sign, and they must meet before $z$.

@@

  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
  Their weights must be of opposite sign, otherwise we can inductively reapplied the same argument to their suffixes.
  Let $\rho_1=\rho_1'\rho_1''$.
  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
  are from $m$ to $z$ going through $y$, but with weights of opposite sign (as $\rho'_1$ and $\rho'_2$ have opposite sign).
  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$. It means that we have a pair of compensating paths from $m$ tp $z$, and thus $y \in X$, a contradiction with $y \in Y_+$. 
\end{proof}

@@

We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same sign:

\begin{lemma}
	\label{lemma11}
	Let $y \in Y_-$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
	of paths with weights of same sign with $\rho_1$ from $m$ to $y$ and 
	with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

@@

As in the proof of Theorem \ref{thm:2}, we can then optimize $Y$ first on its own (considering the sign of every node), and consider its (direct and indirect) contribution to $z$ as biases, before optimizing the rest of the network.
This is exactly what $\MILP_X$ is doing:
the bias from each node of $Y$ comes from the bounds on nodes (of $Y$) computed inductively in the previous layers, and then there is a global optimization of the rest of the network (set of nodes $X$ whose ReLU are encoded exactly in $\MILP_X$).

@@

	\begin{proof}
	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$. Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
	\end{proof}

@@

			Therefore, choose a path $Q$ from input to output with nonzero weight and disjoint from $P,P''$. Now, since weights of $P,P''$ have different signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path. This means $a$ will be opened.

@@

			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
			wrt node $z$. As proved earlier, $Z$ is suffix closed, i.e. if $m<n<z$ with $m \in Z$, then $n \in Z$. We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative sign. $X$ can intersect both $Z_+$ and $Z_-$.
			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.
			We denote $Y=Y_+ \sqcup Y_-$.

@@

\begin{proof}
			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite sign. 
			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight. Depending on the sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$. We call $X_*$ this subset $X$.
\end{proof}

@@

\begin{lemma}
	\label{lemma10}
		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
		of paths  with weights of opposite sign with $\rho_1$ from $m$ to $y$ and 
		with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

\begin{proof}
  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
  Hence $\rho_1 \rho, \rho_2$ have opposite sign, and they must meet before $z$.

@@

  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
  Their weights must be of opposite sign, otherwise we can inductively reapplied the same argument to their suffixes.
  Let $\rho_1=\rho_1'\rho_1''$.
  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
  are from $m$ to $z$ going through $y$, but with weights of opposite sign (as $\rho'_1$ and $\rho'_2$ have opposite sign).
  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$. It means that we have a pair of compensating paths from $m$ to $z$, and thus $y \in X$, a contradiction with $y \in Y_+$. 
\end{proof}

@@

To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the sign of every node): we first maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that 
$S(n)=-1$ at the same time, i.e., with the same input values. And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.

@@

	\begin{proof}
	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same sign, 
	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite sign than $\rho_1$. Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite sign.
	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite sign. 
	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
	\end{proof}

>>>>

We fix a target node $z$.
We now define the partial influence sign function $S^z$, denoted $S$ when $z$ is clear from the context:

\begin{definition}
	\label{sign_of_nodes}
	We define the partial influence sign function $S$ on node $n$: 	
	\begin{enumerate}
		\item $S(n)=0$ if all path from $n$ to $z$ have weight $0$; 
		\item $S(n)=1$ if all path from $n$ to $z$ have non-negative weight, and at least one path has a positive weight; 
		\item $S(n)=-1$ if all path from $n$ to $z$ have non-positive weight, and at least one path has a negative weight. 
	\end{enumerate}
\end{definition}

@@

\begin{proof}
	If $S(n) \neq 0$, then there is a path $\pi$ from $n$ to the output node $z$ with a nonzero weight of the same influence sign as $S(n)$. 
	So there is a non zero path from $m$ to $z$: $(m n) \pi$, whose influence sign is 
	$S(n)\mathrm{Sign}(W_{n m})$. As there is no compensation, $S(m)=S(n)\mathrm{Sign}(W_{n m})$.
	\hfill $\square$
\end{proof}

@@

Using the concept of influence sign, we introduce input vectors $\vx^{*}, \vx^{\sharp}$:

@@

	Let $n$ be node of the DNN. We set the target $z=n$ and consider the influence sign function $S^z=S^n=S$ corresponding to that node. By definition, $S(n)=1$.

@@

	\begin{proof}
		By contradiction, if there is a weak compensating pair of two paths, $\rho_1,\rho_2$, 
		then consider the common nodes by increasing layer $n_1 \cdots n_k$ in $\rho_1,\rho_2$ (including the initial and final nodes).
		Assume that there is no compensating pair.
		It means that all the segment of $\rho_1,\rho_2$ from $n_i$ to $n_{i+1}$ have the same influence sign (they have no nodes in common but the initial and final nodes).
		Hence $\rho_1$ and $\rho_2$ have the same influence sign, a contradiction with $\rho_1,\rho_2$ being a weakly compensating pair. 
	\end{proof}

@@

			Recall the influence sign function of nodes from Definition \ref{sign_of_nodes}. 
			Because weakly compensating paths are allowed, the influence sign function is no longer defined on all nodes. $S$ is defined for all nodes from which there is no weakly compensating pairs of paths to $z$. In particular, $S$ is defined on all nodes of $I$.

@@

			\begin{proof}
				By contradiction, assume that there exists two paths $\rho_1,\rho_2$ from 
				$n$ to $z$ with (strictly) different influence signs. The pair $\langle a_i,n\rangle \cdot \rho_1$ and $\langle a_i,n\rangle \cdot \rho_2$ is compensating, a contradiction with $a_i\in I$. 
			\end{proof}

@@

				(2) If $S(c)=1$, then we have the following:	\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c) \leq constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^0_I,\boldsymbol{x}^0_J}(b)),
				\end{align*}where $\B$ means one of $\UB$ or $\LB$ depending on the influence sign of $W_{bc}$: if $W_{bc}$ is positive, then $\UB$, otherwise $\LB$. Notice that all $b$ displayed are that $S(b)$ defined, because if $S(b)$ undefined, then for fixed $\vx_J$, value of $b$ is fixed and will be put into the constant.

				Now by induction hypothesis part 2, if $S(b)=1$, then $\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\max_{\vx_I}\UB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$; and if $S(b)=-1$, $\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)=\min_{\vx_I}\LB_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)$. Moreover, since $S(c)=1$, $S(b)$ and $W_{bc}$ have the same influence sign. And both $\ReLU$ and $\mathrm{AppB}$ are non-decreasing functions. Combining all these facts, we have:\begin{align*}
					\mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^0_I}(c)\leq 
					&constant + \sum_{b\in B_{open}\cap l_i} W_{bc}\ReLU(\B_{\boldsymbol{x}^*_I,\boldsymbol{x}^0_J}(b)) + \sum_{b\in B_{pure}\cap l_{i}} W_{bc} \mathrm{AppB}(\B_{\boldsymbol{x}^*_I}(b))\\
					= & \mathrm{UB}_{\boldsymbol{x}^0_J,\boldsymbol{x}^*_I}(c). 
				\end{align*}  This is the first equal.

@@

\begin{proof}
Let $(s,t)$ be the source and the target of $(\rho_1,\rho_2)$.
Let an input $a$ such that $a<s$ with path $\rho_0$ between $a$ and $s$,
and $\rho_3$  from $t$ to $z$.
Applying (H1) to the pair 
$(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$, 
we have another (non zero weight) path $\rho'$ from $a$ to $z$ totally disjoint with these two path.
The weights of $(\rho_0 \cdot \rho_1 \cdot \rho_3, \rho_0\cdot \rho_2 \cdot \rho_3)$
are of opposite influence sign because $(\rho_1,\rho_2)$ is weakly compensating, so one of them must be of opposite influence sign than the weight of $\rho'$. Say its $\rho = \rho_0 \cdot \rho_1 \cdot \rho_3$
else we pick $\rho=\rho_0\cdot \rho_2 \cdot \rho_3$.
Then $(\rho,\rho')$ is a pair of compensating path from $a$ to $z$, and as $n$ is neither an input nor $z$, it is strictly on $\rho$.
\end{proof}

@@

			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
			wrt node $z$. As proved earlier, $Z$ is suffix closed, i.e. if $m<n<z$ with $m \in Z$, then $n \in Z$. We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative influence signs. They form 2 independent subnetworks of the DNN.
			$X$ can intersect both $Z_+$ and $Z_-$.
			For nodes not in $Z$: some may be in $X$, and some may be out of $X$.
			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.

			Because of (H1), nodes not in $Z$ (and not in the inputs) are in $X$:
			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite influence sign. 
			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight. Depending on the influence sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$. We call $X_*$ this subset $X$.

\begin{lemma}
	\label{lemma10}
		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
		of paths  with weights of opposite influence sign with $\rho_1$ from $m$ to $y$ and 
		with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

\begin{proof}
  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
  Hence $\rho_1 \rho, \rho_2$ have opposite influence sign, and they must meet before $z$.

@@

  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
  Their weights must be of opposite influence sign, otherwise we can inductively reapplied the same argument to their suffixes.
  Let $\rho_1=\rho_1'\rho_1''$.
  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
  are from $m$ to $z$ going through $y$, but with weights of opposite influence sign (as $\rho'_1$ and $\rho'_2$ have opposite influence sign).
  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$. It means that we have a pair of compensating paths from $m$ tp $z$, and thus $y \in X$, a contradiction with $y \in Y_+$. 
\end{proof}

@@

We have the same results for $y \in Y_-$, for paths $\rho_1, \rho_2$ of same influence sign:

\begin{lemma}
	\label{lemma11}
	Let $y \in Y_-$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
	of paths with weights of same influence sign with $\rho_1$ from $m$ to $y$ and 
	with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

@@

As in the proof of Theorem \ref{thm:2}, we can then optimize $Y$ first on its own (considering the influence sign of every node), and consider its (direct and indirect) contribution to $z$ as biases, before optimizing the rest of the network.
This is exactly what $\MILP_X$ is doing:
the bias from each node of $Y$ comes from the bounds on nodes (of $Y$) computed inductively in the previous layers, and then there is a global optimization of the rest of the network (set of nodes $X$ whose ReLU are encoded exactly in $\MILP_X$).

@@

	\begin{proof}
	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same influence sign, 
	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite influence sign than $\rho_1$. Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite influence sign.
	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite influence sign. 
	We then apply Lemma \label{lemma11}, inductively then applying Lemma \label{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
	\end{proof}

@@

			Therefore, choose a path $Q$ from input to output with nonzero weight and disjoint from $P,P''$. Now, since weights of $P,P''$ have different influence signs, and $a$ is in both paths, whatever the weight of $Q$ is, $Q$ and one of  $P$ or $P''$ can form a compensating pair (not weak compensating pair anymore, because $Q$ is disjoint with $P,P''$), and $a$ is in a path. This means $a$ will be opened.

@@

			Let $Z$ be the subset of nodes $n$ of the DNN such that $S$ is defined on $n$ 
			wrt node $z$. As proved earlier, $Z$ is suffix closed, i.e. if $m<n<z$ with $m \in Z$, then $n \in Z$. We can partition $Z = Z_{+} \sqcup Z_{-}$, for positive and negative influence signs. $X$ can intersect both $Z_+$ and $Z_-$.
			We call $X_+ = Z_+ \cap X$ and $X_-=Z_- \cap X$, as well as 
			defined $Y_+,Y_-$ such that $Z_+ = X_+ \sqcup Y_+$ and $Z_- = X_- \sqcup Y_-$.
			We denote $Y=Y_+ \sqcup Y_-$.

@@

\begin{proof}
			node $n \notin Z$ implies the existence of two path $\rho_1,\rho_2$ (not necessarily disjoint) to $z$, with opposite influence sign. 
			Take an input node $a$ reaching $n$ with path $\rho$ with non zero weight.
			Then using (H1), we get a third path $\rho_3$ disjoint from $\rho \cdot \rho_1$ and from $\rho \cdot \rho_2$ with non-zero weight. Depending on the influence sign of $weight(\rho_3)$, it will form a compensating pair of path to $z$ either with $\rho \cdot \rho_1$ or with $\rho \cdot \rho_2$, hence $n$ will be in $X$. We call $X_*$ this subset $X$.
\end{proof}

@@

\begin{lemma}
	\label{lemma10}
		Let $y \in Y_+$. Then for all $m$, there does not exist a pair $(\rho_1,\rho_2)$ 
		of paths  with weights of opposite influence sign with $\rho_1$ from $m$ to $y$ and 
		with $\rho_2$ from $m$ to $z$ (even non disjoint).
\end{lemma}

\begin{proof}
  $y \notin X$, so it is not on a pair of compensating pair with target $z$.
  Let $\rho$ be a path from $y$ to $z$ (it has positive weight has $y \in Z_+$).
  Hence $\rho_1 \rho, \rho_2$ have opposite influence sign, and they must meet before $z$.

@@

  Hence $\rho_1$ must meet $\rho_2$ (that is before or at $y$).
  Their weights must be of opposite influence sign, otherwise we can inductively reapplied the same argument to their suffixes.
  Let $\rho_1=\rho_1'\rho_1''$.
  Both $\rho_1 \cdot \rho$ and $\rho_2' \cdot \rho_1'' \cdot \rho$
  are from $m$ to $z$ going through $y$, but with weights of opposite influence sign (as $\rho'_1$ and $\rho'_2$ have opposite influence sign).
  Now, by $(H1)$, there exists a path $\rho_3$ disjoint from $\rho_1 \cdot \rho$ and$\rho_2' \cdot \rho_1'' \cdot \rho$ from $m$ to $z$. It means that we have a pair of compensating paths from $m$ to $z$, and thus $y \in X$, a contradiction with $y \in Y_+$. 
\end{proof}

@@

To prove Theorem \ref{th2}, we can then optimize $Y$ first on its own (considering the influence sign of every node): we first maximize all $n$ such that $S(n)=1$ and minimize all $n$ such that 
$S(n)=-1$ at the same time, i.e., with the same input values. And for every node $n$ in $Y$, the value computed is the same as actual lower and upper bounds of $n$.

@@

	\begin{proof}
	By contradiction, assume that there exist nodes $m, n^+ \in Y_+$ and  $n^
	- \in Y_-$, such that there are two non-zero weight paths $\rho_1$ from $m$ to $n^+$ and $\rho_2$ from $n$ to $n^-$ Assume first that the weights of $\rho_1,\rho_2$ have the same influence sign, 
	in which case it gives us a path $\rho_2 \rho_3$  from $m$ to $z$ of opposite influence sign than $\rho_1$. Applying Lemma \ref{lemma10}, we have prefixes $\rho'_1,\rho'_2$ of $\rho_1,\rho_2$ ending in the same state $m'$, and with weights of opposite influence sign.
	So we are left with path from $m'$ to $Y_-,Y_+$ of opposite influence sign. 
	We then apply Lemma \ref{lemma11}, inductively then applying Lemma \ref{lemma10} on the suffices etc. We obtain a contradiction to the existence of $m$ with $m<n^+$ and $m<n^-$. 
	\end{proof}
